Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-22 bdcloud_paper/latex/paper.tex
Edits to MSM transition probabilities

Markov Models are used to model the customer's purchasing behavior for each item category.  Each state corresponds to an item in that category. The transition probabilities are assigned according to the customer's buying habits.  For example, if a customer tends to buy the same brand of dog food repeatedly, the outgoing edges to all products of the same brand as the product in the current state will be higher than those for other brands' products. If the customer does not care about flavor, the outgoing edges to all products from the current brand will be equal, otherwise the edge weights can be adjusted to prefer a specific combination of brand and flavor.  Likewise, if a customer cares more about flavor or cost, the edge weights will be assigned appropriately.  To simulate an item purchase, the Markov model is transitioned forward by one state.  The current states of the Markov models are kept between purchases.

@@

\begin{align*}
Pr(X_{n+1}&=x|X_n=y) = \\
& \left\{ 
  \begin{array}{l l}
   (1.0 - w_l) W^{-1} \sum_f w_f w_{f,s}(x, y)  & \quad \text{if $x \neq y$}\\
   w_l & \quad \text{if $x = y$}
  \end{array} \right.
\end{align*}

\begin{align*}
&w_l \sim N(\mu, \sigma^2) \\
&w_f \sim N(\mu, \sigma^2) \\
&w_{f, s} \sim N(\mu, \sigma^2)
\end{align*}

@@

The current implementation was prototyped in Python.  We are working to implement the model using in Hadoop and Spark.  We will commit the resulting implementations to the Apache BigTop project to enable ease of access and immediate benefit to current users.

>>>>

Markov Models are used to model the customer's purchasing behavior for each item category.  Each state $X_n$ corresponds to an item in that category. The customer's buying habits are determined by the transition probabilities (Eq.~\ref{eq:transition_probabilities}).  The transition probabilities depend on three types of parameters: loopback weight $w_l$ indicating the probability of purchasing the same item again, weight $w_f$ of a particular field $f$, and the weight $w_{f,s}$ when two items $x$ and $y$ have the same value for the field $f$.

\begin{align} \label{eq:transition_probabilities}
Pr(X_{n+1}&=x|X_n) = \nonumber \\
& \left\{ 
  \begin{array}{l l}
   (1.0 - w_l) W^{-1} \sum_f w_f w_{f,s}(x, y)  & \quad \text{if $x \neq X_n$}\\
   w_l & \quad \text{if $x = X_n$}
  \end{array} \right.
\end{align}

\textcolor{red}{todo}

\textcolor{red}{todo}

The weights $w_l$, $w_f$, and $w_{f, s}$ are chosen randomly for each customer.

@@

\begin{align} \label{eq:item-weights}
&w_l \sim N(\mu, \sigma^2) \nonumber \\
&w_f \sim N(\mu, \sigma^2) \nonumber \\
&w_{f, s} \sim N(\mu, \sigma^2)
\end{align}

\textcolor{red}{reorder so that probilities describe habits}

For example, if a customer tends to buy the same brand of dog food repeatedly, the outgoing edges to all products of the same brand as the product in the current state will be higher than those for other brands' products. If the customer does not care about flavor, the outgoing edges to all products from the current brand will be equal, otherwise the edge weights can be adjusted to prefer a specific combination of brand and flavor.  Likewise, if a customer cares more about flavor or cost, the edge weights will be assigned appropriately.

To simulate an item purchase, the Markov model is transitioned forward by one state.  The current states of the Markov models are kept between purchases.

@@

The current implementation was prototyped in Python.  We are working to implement the model using Hadoop and Spark.  We will commit the resulting implementations to the Apache BigTop project to enable ease of access and immediate benefit to current users.
